---
title: "5205_final"
output: html_document
---

# In this project, we will compare people's attitude to COVID in two different time based on two datasets, one is Mar-Apr 2020, when COVID just started, and the other is from late October 2021 to Jan 2022, when a new variant with stronger infectivity but low serve rate, Omicron was founded. These two different datasets can represent people's attitude at the begining of the COVID as well as the end of the COVID.

```{r, include=FALSE}
setwd("C:/Users/white/Desktop/")
data = read.csv("omicron_tweets.csv")
```

```{r}
library(circlize)
library(readr)        # reads in CSV
library(ggplot2)      # plot library
library(tidyverse)    # for data manipulation
library(gridExtra)    # multiple plots in 1
library(magick)       # attach dope image for visual
library(scales)       # show the colors
library(ggrepel)      # for graph repel (labels)
library(repr)         # resize graphs
library(naniar)       # to check for missing data
library(lubridate)    # for date and time
library(tm)
library(tidytext)     # text preprocessing
library(textdata)     # text preprocessing
library(reshape2)
library(knitr)
library(grid)
library(igraph)
library(ggraph)
library(ggsci)
library(stringr)
library(sjmisc)
library(magick)
library(htmlwidgets)
library(VIM)          # missing values visual
library(textmineR)
library(wordcloud)
library(wordcloud2)
library(ggthemes)
```

```{r}
bing = as.data.frame(get_sentiments('bing'))
get_sentiments('bing') %>% 
  group_by(sentiment) %>%
  count()
```

```{r}
unnest_tweets = data %>%
  mutate(text = as.character(data$text)) %>%
  unnest_tokens(word, text)
```

```{r, include=FALSE}
tweets_words = data %>%
  group_by(user_name) %>%
  unnest_tokens(output = word, input = text) %>%
  ungroup() %>%
  mutate(row=1:n())
as.data.frame(tweets_words)[c('user_name', 'word')]
```

```{r}
afinn = read.table('https://raw.githubusercontent.com/pseudorational/data/master/AFINN-111.txt',header = F,sep = '\t',col.names = c('word','value'))
```

```{r}
afinn %>%
  group_by(value)%>%
  count()
```
# score all words
```{r}
tweets_words %>%
  inner_join(afinn,by = 'word')%>%
  select('value')%>%
  ggplot(aes(x=value))+geom_histogram()+theme_wsj()+labs(title = "Words Scoring")
```
# score each tweets
```{r}
tweets_words %>%
  left_join(afinn,by = 'word')%>%
  group_by(user_name)%>%
  summarize(value = mean(value,na.rm=T))%>%
  ungroup()%>%
  select('user_name','value')%>%
  ggplot(aes(x=value))+geom_histogram()+theme_wsj()+
  scale_fill_manual(values = c('green','blue'))+labs(title = "Tweets Scoring")
  
```
# sentiment score
```{r}
tweets_words %>%
  inner_join(afinn,by = 'word')%>%
  group_by(user_name)%>%
  summarize(tweet_sentiment = mean(value,na.rm=T))%>%
  ungroup()
```

```{r}
tweets_words %>%
  inner_join(afinn,by = 'word')%>%
  group_by(user_name)%>%
  summarize(tweet_sentiment = mean(value,na.rm=T))%>%
  ungroup()%>%
  summarize(Overall_Sentiment=mean(tweet_sentiment,na.rm=T))
```
# emotion of tweets
```{r}
nrc = read.table(file = 'https://raw.githubusercontent.com/pseudorational/data/master/nrc_lexicon.txt',header = F,col.names = c('word','sentiment','num'),sep = '\t'); nrc = nrc[nrc$num!=0,]; nrc$num = NULL
```

```{r}
nrc%>%
  group_by(sentiment)%>%
  count()
```

```{r}
library(RColorBrewer)
tweets_words %>%
  inner_join(get_sentiments('nrc'),by = 'word')%>%
  select('sentiment')%>%
  group_by(sentiment)%>%
  summarize(freq=n())%>%
  ungroup() %>%
  ggplot(aes(x=reorder(sentiment,freq),y=freq,fill=freq))+geom_bar(position='dodge',stat='identity')+xlab('Sentiment')+ylab('Frequency')+coord_flip()+labs(title = "Sentiment Frequency")

```
```{r}
tweets_words %>% 
  inner_join(nrc, "word") %>% 
  count(sentiment, word, sort=T) %>%
  group_by(sentiment) %>% 
  arrange(desc(n)) %>% 
  slice(1:7) %>% 
  
  # Plot:
  ggplot(aes(x=reorder(word, n), y=n)) +
  geom_col(aes(fill=sentiment), show.legend = F) +
  facet_wrap(~sentiment, scales = "free_y", nrow = 2, ncol = 5) +
  coord_flip() +
  theme(axis.text.x = element_blank()) +
  labs(x="Word", y="Frequency", title="Top Words Distribution by Sentiments")
```

```{r}
wordcloud_data= 
  tweets_words %>%
  anti_join(rbind(stop_words,c('trump','SMART')),by = 'word')%>%
  inner_join(get_sentiments('bing'),by='word')%>%
  count(sentiment,word,sort=T)%>%
  ungroup()%>%
  spread(key = sentiment,value = 'n',fill = 0)
wordcloud_data= as.data.frame(wordcloud_data)
rownames(wordcloud_data) = wordcloud_data[,'word']
wordcloud_data = wordcloud_data[,c('positive','negative')]
comparison.cloud(wordcloud_data,scale=c(2,0.5),max.words = 200,rot.per = 0, title.size = 2)  
```
# sort country data
```{r}
tweets_location = data %>%
                        # convert to lower case
                        mutate(user_location = tolower(user_location)) %>%
                        group_by(user_location) %>%
                        summarise(n = n(), .groups = "drop_last") %>%
                        arrange(desc(n))
tweets_location$country <- NA
```
# mapping location into country
```{r}
tweets_location <- tweets_location %>%
                        mutate(country = ifelse(grepl("india", user_location), "India", country),
                               country = ifelse(grepl("delhi", user_location), "India", country),
                               country = ifelse(grepl("mumbai", user_location), "India", country),
                               country = ifelse(grepl("bengaluru", user_location), "India", country),
                               country = ifelse(grepl("bangalore", user_location), "India", country),
                               country = ifelse(grepl("bhubaneswar", user_location), "India", country),
                               country = ifelse(grepl("hyderabad", user_location), "India", country),
                               country = ifelse(grepl("china", user_location), "China", country),
                               country = ifelse(grepl("beijing", user_location), "China", country),
                               country = ifelse(grepl("hong kong", user_location), "Hong Kong", country),
                               country = ifelse(grepl("singapore", user_location), "Singapore", country),
                               country = ifelse(grepl("australia", user_location), "Australia", country),
                               country = ifelse(grepl("melbourne", user_location), "Australia", country),
                               country = ifelse(grepl("sydney", user_location), "Australia", country),
                               country = ifelse(grepl("canada", user_location), "Canada", country),
                               country = ifelse(grepl("africa", user_location), "Africa", country),
                               country = ifelse(grepl("england", user_location), "UK", country),
                               country = ifelse(grepl("united kingdom", user_location), "UK", country),
                               country = ifelse(grepl("london", user_location), "UK", country),
                               country = ifelse(grepl("uk", user_location), "UK", country),
                               country = ifelse(grepl("united states", user_location), "US", country),
                               country = ifelse(grepl("usa", user_location), "US", country),
                               country = ifelse(grepl("us", user_location), "US", country),
                               country = ifelse(grepl("washington", user_location), "US", country),
                               country = ifelse(grepl("new york", user_location), "US", country),
                               country = ifelse(grepl("angeles", user_location), "US", country),
                               country = ifelse(grepl("atlanta", user_location), "US", country),
                               country = ifelse(grepl("california", user_location), "US", country),
                               country = ifelse(grepl("chicago", user_location), "US", country),
                               country = ifelse(grepl("boston", user_location), "US", country),
                               country = ifelse(grepl("philadelphia", user_location), "US", country),
                               country = ifelse(grepl("diego", user_location), "US", country),
                               country = ifelse(grepl("seattle", user_location), "US", country),
                               country = ifelse(grepl("texas", user_location), "US", country),
                               country = ifelse(grepl("nyc", user_location), "US", country),
                               country = ifelse(grepl("vegas", user_location), "US", country),
                               country = ifelse(grepl("francisco", user_location), "US", country),
                               country = ifelse(grepl("florida", user_location), "US", country),
                               country = ifelse(grepl("dallas", user_location), "US", country),
                               country = ifelse(grepl("denver", user_location), "US", country),
                               country = ifelse(grepl("worldwide", user_location), "NoCountry", country),
                               country = ifelse(grepl("global", user_location), "NoCountry", country),
                               country = ifelse(grepl("earth", user_location), "NoCountry", country),
                               country = ifelse(grepl("everywhere", user_location), "NoCountry", country),
                               country = ifelse(grepl("nigeria", user_location), "Nigeria", country),
                               country = ifelse(grepl("kenya", user_location), "Kenya", country),
                               country = ifelse(grepl("switzerland", user_location), "Switzerland", country),
                               country = ifelse(grepl("ireland", user_location), "Ireland", country),
                               country = ifelse(grepl("canada", user_location), "Canada", country),
                               country = ifelse(grepl("toronto", user_location), "Canada", country),
                               country = ifelse(grepl("philippines", user_location), "Philippines", country),
                               country = ifelse(grepl("malaysia", user_location), "Malaysia", country),
                               country = ifelse(grepl("ny", user_location), "US", country),
                               country = ifelse(grepl("nj", user_location), "US", country),
                               country = ifelse(grepl("pa", user_location), "US", country),
                               country = ifelse(grepl("ohio", user_location), "US", country),
                               country = ifelse(grepl("california", user_location), "US", country),
                               country = ifelse(grepl("silicon valley", user_location), "US", country),
                               country = ifelse(grepl("ak", user_location), "US", country),
                               country = ifelse(grepl("tx", user_location), "US", country),
                               country = ifelse(grepl("va", user_location), "US", country)
)
```

# a summary of countries
```{r}
table(tweets_location$country)
```
# plot tweets locations
```{r}
tweets_location %>%
    group_by(country) %>%
    summarise(n = n(), .groups = "drop_last") %>%
    filter(country != "NA") %>%

    ggplot(aes(x = reorder(country, n), y = n, fill=n)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_gradient(guide="none") +
    geom_label(aes(label=n), size=2, fill="white") +
    labs(x="Number of Tweets", y="Country",title = "Countries/Regions Location for Tweets") +
    theme(axis.text.x = element_blank(),
                     axis.title = element_blank())
```
# Sorting unnest_tweets country
```{r}
unnest_tweets <- data %>% 
    mutate(text = as.character(data$text)) %>% 
    unnest_tokens(word, text)
unnest_tweets$country <- NA
```
# mapping location into country
```{r}
major_country = unnest_tweets %>%
  mutate(country = ifelse(grepl("india", user_location), "India", country),
                               country = ifelse(grepl("delhi", user_location), "India", country),
                               country = ifelse(grepl("mumbai", user_location), "India", country),
                               country = ifelse(grepl("bengaluru", user_location), "India", country),
                               country = ifelse(grepl("bangalore", user_location), "India", country),
                               country = ifelse(grepl("bhubaneswar", user_location), "India", country),
                               country = ifelse(grepl("hyderabad", user_location), "India", country),
                               country = ifelse(grepl("china", user_location), "China", country),
                               country = ifelse(grepl("beijing", user_location), "China", country),
                               country = ifelse(grepl("hong kong", user_location), "Hong Kong", country),
                               country = ifelse(grepl("singapore", user_location), "Singapore", country),
                               country = ifelse(grepl("australia", user_location), "Australia", country),
                               country = ifelse(grepl("melbourne", user_location), "Australia", country),
                               country = ifelse(grepl("sydney", user_location), "Australia", country),
                               country = ifelse(grepl("canada", user_location), "Canada", country),
                               country = ifelse(grepl("africa", user_location), "Africa", country),
                               country = ifelse(grepl("england", user_location), "UK", country),
                               country = ifelse(grepl("united kingdom", user_location), "UK", country),
                               country = ifelse(grepl("london", user_location), "UK", country),
                               country = ifelse(grepl("uk", user_location), "UK", country),
                               country = ifelse(grepl("united states", user_location), "US", country),
                               country = ifelse(grepl("usa", user_location), "US", country),
                               country = ifelse(grepl("us", user_location), "US", country),
                               country = ifelse(grepl("washington", user_location), "US", country),
                               country = ifelse(grepl("new york", user_location), "US", country),
                               country = ifelse(grepl("angeles", user_location), "US", country),
                               country = ifelse(grepl("atlanta", user_location), "US", country),
                               country = ifelse(grepl("california", user_location), "US", country),
                               country = ifelse(grepl("chicago", user_location), "US", country),
                               country = ifelse(grepl("boston", user_location), "US", country),
                               country = ifelse(grepl("philadelphia", user_location), "US", country),
                               country = ifelse(grepl("diego", user_location), "US", country),
                               country = ifelse(grepl("seattle", user_location), "US", country),
                               country = ifelse(grepl("texas", user_location), "US", country),
                               country = ifelse(grepl("nyc", user_location), "US", country),
                               country = ifelse(grepl("vegas", user_location), "US", country),
                               country = ifelse(grepl("francisco", user_location), "US", country),
                               country = ifelse(grepl("florida", user_location), "US", country),
                               country = ifelse(grepl("dallas", user_location), "US", country),
                               country = ifelse(grepl("denver", user_location), "US", country),
                               country = ifelse(grepl("worldwide", user_location), "NoCountry", country),
                               country = ifelse(grepl("global", user_location), "NoCountry", country),
                               country = ifelse(grepl("earth", user_location), "NoCountry", country),
                               country = ifelse(grepl("everywhere", user_location), "NoCountry", country),
                               country = ifelse(grepl("nigeria", user_location), "Nigeria", country),
                               country = ifelse(grepl("kenya", user_location), "Kenya", country),
                               country = ifelse(grepl("switzerland", user_location), "Switzerland", country),
                               country = ifelse(grepl("ireland", user_location), "Ireland", country),
                               country = ifelse(grepl("canada", user_location), "Canada", country),
                               country = ifelse(grepl("toronto", user_location), "Canada", country),
                               country = ifelse(grepl("philippines", user_location), "Philippines", country),
                               country = ifelse(grepl("malaysia", user_location), "Malaysia", country),
                               country = ifelse(grepl("ny", user_location), "US", country),
                               country = ifelse(grepl("nj", user_location), "US", country),
                               country = ifelse(grepl("pa", user_location), "US", country),
                               country = ifelse(grepl("ohio", user_location), "US", country),
                               country = ifelse(grepl("california", user_location), "US", country),
                               country = ifelse(grepl("silicon valley", user_location), "US", country),
                               country = ifelse(grepl("ak", user_location), "US", country),
                               country = ifelse(grepl("tx", user_location), "US", country),
                               country = ifelse(grepl("va", user_location), "US", country)
)
```
#filter out top countires
```{r}
filter = major_country %>%
  filter(country %in% c("US", "UK", "India", "NoCountry"))
```

```{r}
total_bing <- filter %>% 
    inner_join(bing, by="word") %>%
    count(country) %>% 
    group_by(country) %>% 
    summarise(total_tweets = sum(n), .groups = "drop_last")

```

```{r}
set.seed(1009)
to_plot <- filter %>% 
    # get 'bing' and filter the data
    inner_join(bing, by="word") %>%

    # sum number of words per sentiment and country
    count(sentiment, country) %>% 
    group_by(country, sentiment) %>% 
    summarise(sentiment_sum = sum(n), .groups = "drop_last") %>% 
    inner_join(total_bing, by="country") %>% 
    mutate(sentiment_perc = sentiment_sum/total_tweets) %>% 
    select(country, sentiment, sentiment_perc)
circos.clear()
circos.par(gap.after = c(rep(2, length(unique(to_plot[[1]])) - 1), 15,
                         rep(2, length(unique(to_plot[[2]])) - 1), 15), gap.degree=2)

chordDiagram(to_plot, transparency = 0.2, annotationTrack = c("name", "grid"),
             annotationTrackHeight = c(0.03, 0.06))
title("Relationship between Sentiment and Countries")
```
# implementing an interactive word cloud
```{r}
frequentTerms <- function(text){
  
  # create the matrix
  s.cor <- VCorpus(VectorSource(text))
  s.cor.cl <- cleanCorpus(s.cor)
  s.tdm <- TermDocumentMatrix(s.cor.cl)
  s.tdm <- removeSparseTerms(s.tdm, 0.999)
  m <- as.matrix(s.tdm)
  word_freqs <- sort(rowSums(m), decreasing = T)
  
  # change to dataframe
  dm <- data.frame(word=names(word_freqs), freq=word_freqs)
  
  return(dm)
}
cleanCorpus <- function(text){
  # punctuation, whitespace, lowercase, numbers
  text.tmp <- tm_map(text, removePunctuation)
  text.tmp <- tm_map(text.tmp, stripWhitespace)
  text.tmp <- tm_map(text.tmp, content_transformer(tolower))
  text.tmp <- tm_map(text.tmp, removeNumbers)
  
  # removes stopwords
  stopwords_remove <- c(stopwords("en"), c("thats","weve","hes","theres","ive","im",
                                                "will","can","cant","dont","youve","us",
                                                "youre","youll","theyre","whats","didnt","https", "tco"))
  text.tmp <- tm_map(text.tmp, removeWords, stopwords_remove)

  return(text.tmp)
}
wc_data <- frequentTerms(tweets_words$word) %>% filter(word != "covid")

a <- wordcloud2(wc_data, size=1.6, minSize = 0.9, 
            color='random-light', backgroundColor="black", shape="diamond", 
            fontFamily="HersheySymbol")
library(webshot)
 webshot::install_phantomjs()
 saveWidget(a,"1.html",selfcontained = F)
 webshot::webshot("1.html","1.png",vwidth = 1992, vheight = 1744, delay =10)
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


